Spin canonical divisors of log stacky curves

### 2015-06-26 stacky_write_up/spin_cring.tex
editing raise stacky order

This theorem is proven in three different genus cases, each of
which use similar inductive processes. The high genus case is
proven in Theorem ~\ref{thm:high_generators_relations}. In Theorem
~\ref{thm:g_1_generators_relations} and Theorem
~\ref{thm:g_0_generators_relations}, we also give the respective
genus one and genus zero results after using a similar induction
process while dealing with more complicated base cases and
exceptional cases.

@@

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
\end{enumerate}

@@

Transition words.
\todo{transition!}

\ssec{Inductive Lemma: Raising stabilizer orders}
\label{ssec:ram_orders}
In this section, we aim to prove the inductive theorem, Theorem
~\ref{lem:raise-stacky-order}. Under fairly general
conditions, this theorem will allow us to show that if Theorem ~\ref
{lem:raise-stacky-order} holds for a curve with signature
$(0;e_1', \ldots, e_r';0)$ then it also holds for a curve with
signature $(0; e_1, \ldots, e_r; 0)$ with $e_i' - e_i \in \{0 , 2\}$.

@@

\begin{defn}
\label{defn:admissible}
Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
curves, with the same stacky points $Q_1, \ldots, Q_r$. Suppose
there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where

@@

@@

@@

\begin{rem}
\label{rem:three-cases}
For the purposes of our induction, we will often be adding in a single 
stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases:
\begin{enumerate}
	\item $g = 0, \delta = 0, $ and $r \geq 5$
	\item $g = 1, \delta = 0,$ and $ r \geq 2$
	\item $g \geq 2, \delta$ arbitrary, and $r \geq 1$.
\end{enumerate}
\end{rem}

@@

\ssec{Main Theorem for High Genus}
\label{ssec:main_g_high}

\begin{thm}
\label{thm:high_generators_relations}
Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\begin{thm}
\label{thm:g_1_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
If $g = 1$, then the canonical ring
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
\end{align*}

@@

\begin{rem}
In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g_1_generators_relations}, proof of Theorem ~\ref{thm:g_1_generators_relations} yields an explicit procedure for computing those minimal generators and relations. That, is one can start with the generators and relations for the base cases, and then inductively add in generators and relations, according to the inductive theorems.
\end{rem}

@@

\iffalse
Through the application of two inductively adding 
points via Lemma ~\ref{lem:sat-3} and inductively raising
stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.
\fi

@@

\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
Then, the canonical ring

>>>>

This theorem is proven in three different genus cases, each of
which use similar inductive processes. The high genus case is
proven in Theorem ~\ref{thm:g-high-main}. In Theorem
~\ref{thm:g-1-main} and Theorem
~\ref{thm:g-0-main}, we also give the respective
genus one and genus zero results after using a similar induction
process while dealing with more complicated base cases and
exceptional cases.

@@

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Notation for Coarse space
	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
\end{enumerate}

@@

\todo{transition!}

\ssec{Raising Stabilizer Orders}
\label{ssec:ram_orders}
In this subsection, we aim to prove Lemma
~\ref{lem:raise-stacky-order}, whose proof is almost identical to that of \cite[Theorem 8.5.7]{vzb:stacky}. In many cases, Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem 
~\ref{thm:main}, holds for a curve with signature
$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta),$ with $e_{k+1}' = \cdots = e_r',$ then Theorem ~\ref{thm:main} also holds for a curve with
signature $(g; e_1', \ldots, e_k',e_{k+1}'+2,\ldots, e_r'+2; \delta).$ In order to state Lemma
~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.

One key difference between the notion of admissibility in Definition ~\ref{defn:admissible} and \cite[Definition 8.5.1]{vzb:stacky} is that in \cite{vzb:stacky}, Voight and Zureick-Brown may assume that $\{P_i\} \cap \Supp(K_X) = \emptyset.$ However, we cannot assume that $\{P_i\} \cap \Supp(L_X) = \emptyset$, as $L_X$ is not necessarily basepoint-free. Therefore, we will have to work with orders of zeros of poles relative to the divisor we are inducting from, instead of relative to the structure sheaf. Hence, we introduce the following notation.

@@

\begin{defn}
\label{defn:admissible}
Let $(\sx', \Delta, L'),(\sx, \Delta , L)$ be log spin
curves, with the same stacky points $Q_1, \ldots, Q_r$. Let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2 \chi_J (i) = e_i$ where

@@

\begin{rem}
Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
\end{rem}

@@

The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}. Lemma ~\ref{lem:admissible_inequality} can be thought of as an analog of \cite[Lemma 8.5.3]{vzb:stacky}

@@

\begin{rem}
\label{rem:three-cases}
For the purposes of our induction, carried out in Theorems ~\ref{thm:g-high-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-0-main}, we will often add in a single
stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases, which we will soon refer to in Lemma ~\ref{lem:raise-stacky-order}:
\begin{enumerate}
	\item $g = 0, e_1 = \cdots = e_r = 3, \delta = 0$ and $r \geq 5$
	\item $g = 1, e_1 = \cdots = e_r = 3, \delta = 0,$ and $ r \geq 2$
	\item $g \geq 2, e_1 = \cdots = e_r = 3, \delta$ arbitrary, and $r \geq 1$.
\end{enumerate}
\end{rem}

@@

\ssec{Main Theorem for High Genus}
\label{ssec:g-high-main}

\begin{thm}
\label{thm:g-high-main}
Let $g \geq 2$ and let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (g; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\begin{thm}
\label{thm:g-1-main}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (1; e_1, \ldots, e_r; \delta)$.
If $g = 1$, then the canonical ring
\begin{align*}
	R(\sx, \Delta, \halfcan) = \bigoplus_{d = 0}^\infty H^0(\sx, \sco(L)^{\otimes d})
\end{align*}

@@

\begin{rem}
In addition to the bound on the degree of the generators and relations, as detailed in Theorem ~\ref{thm:g-1-main}, proof of Theorem ~\ref{thm:g-1-main} yields an explicit procedure for computing those minimal generators and relations. That, is one can start with the generators and relations for the base cases, and then inductively add in generators and relations, according to the inductive theorems.
\end{rem}

@@

\iffalse
Through the application of two inductively adding 
points via Lemma ~\ref{lem:sat-3} and inductively raising
stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
we obtain Theorem ~\ref{thm:g-0-main} for any
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.
\fi

@@

\begin{thm}
\label{thm:g-0-main}
Let $(\sx, \Delta, \halfcan)$ log spin curve over a perfect field $k$,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$.
Then, the canonical ring
